%!TEX program = xelatex

\documentclass{uniquecv}

\usepackage{fontawesome5}
\usepackage{fontspec}
\usepackage[colorlinks]{hyperref}
% ----------------------------------------------------------------------------- %

%\setmonofont{FiraCode}
\begin{document}
\name{Qingyu Wang}
\medskip

\basicinfo{
  \faPhone ~ (+86) 136-5113-2812
  \textperiodcentered\
  \faEnvelope ~ qingyu.wang@aliyun.com
  \textperiodcentered\
  \faGithub ~ github.com/colinaaa
  \textperiodcentered\
  \faBlog ~ \href{https://about.outsiders.top}{\color{black}{blog}}
}

% ----------------------------------------------------------------------------- %

\section{Education}
\dateditem{\textbf{TsingHua University High School} \quad High School}{2012 -- 2018 }
Grade: Top 10\%
\dateditem{\textbf{Huazhong University of Science \& Technology} \quad Computer Science}{2018 -- Now}
Grade: Top 20\% \quad English: CET4-573 \quad CET6-551


% ----------------------------------------------------------------------------- %

\section{Professional Skills}
\smallskip
\textbf{Programming}
\quad C++1a/Golang/TypeScript/React/Linux/Operating System/Data Structure/Computer Networking

\textbf{Tools} \quad \LaTeX/(neo)vim/Git

% ----------------------------------------------------------------------------- %

\section{Internships}
\dateditem{\textbf{Bytedance Inc.} \quad Frontend intern} {Dec. 2020 - Mar. 2021}

\begin{itemize}
  \item Build pages in Douyin.
  \item Participate in development of a hybrid framework ReactLynx.
\end{itemize}

\dateditem{\textbf{Tencent Inc.} \quad Backend intern} {Jul. 2020 - Sept. 2020}

\begin{itemize}
  \item Build a dashboard for Novartis.
  \item Optimize building pipeline of the Projects.
\end{itemize}

% ----------------------------------------------------------------------------- %

\section{Projects}

\datedproject{Unique HR System}{Team Project}{Feb. 2020 - Now}
{\it The Hire Recruitment System for Unique Studio}
\quad \emph{maintainer}
\vspace{0.4ex}

\begin{itemize}
  \item Frontend: React/TypeScript/Redux/RxJS/Material UI
  \item Backend: Node.js/TypeScript/Mongoose/Express.js
\end{itemize}

\datedproject{xv6 Labs}{Class Project}{Sept. 2020 -- Nov. 2020}
{\it MIT 6.S081 Operating System Engineering Labs}
\vspace{0.4ex}
\\
A Operating System labs based on UNIX v6 and RISC-V.
\begin{itemize}
  \item Implement a user space page table, the kernel can access user memory without changing page table.
  \item Implement lazy allocation, delay the allocation of physical memory through page fault.
  \item Implement copy on write, improve the efficiency of fork through page fault and page table.
\end{itemize}

\datedproject{CSAPP Labs}{Class Project}{Jan. 2020 -- Mar. 2020}
{\it CMU 15213 Introduction to Computer System labs}
\vspace{0.4ex}
\begin{itemize}
  \item AMD-64 Assembly / Cache / malloc / Shell
\end{itemize}

% ----------------------------------------------------------------------------- %

\section{Clubs}
\dateditem{\textbf{Unique Studio}}{Oct. 2018 -- Now}

\end{document}
